\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-09-06 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Note sur 10/3
Signed-off-by: Guillaume Daudin <gdaudin@mac.com>
avec le .tex corrigé des bugs

\begin{table}[htbp]
 \centering
\caption{Transport costs estimates: summary} \vspace{5mm} \label{tab:summary_results}
	\input{Table1_reshaped.tex}
		\begin{tablenotes}
		\tiny
		\item Statistics are obtained weighting each observation by its value relative to total trade flows.
		%\item The additive term is expressed in fraction of fas price.
		\item For the  4-digit model, statistics for observed data have been calculated for the same set of years as used for estimation, i.e.
		1974, 1981, 1989, 2001, 2009, 2013, 2017 and 2019
		\item \textbf{Model (a): With ad-valorem transport costs only}
		\item \textbf{Model (b): With additive and ad-valorem transport costs}
	\end{tablenotes}
\end{table}

@@

\begin{table}[htbp]
  \centering
  \caption{Calibration (1)} \label{tab:calib_horsTC}
\begin{center}
	\input{donnees_calibration.tex}
\end{center}
{\parbox[l]{12cm}{ \vspace{4pt}\footnotesize{Notes: $f_x$ can take two values, depending on the share of exporters considered that might differ between the initial steady state (4\%, based on early 1980s' value) and the final steady state (6\%, based on 2000's value.}}}
\end{table}

Following \cite{ghironi}, $f$ such that all firms produce in autarky (i.e., such that $\varphi^{\ast,a} = \varphi_{\text{min}}$. The calibration of the fixed export cost obeys the following logic. As in \cite{ghironi}, $f_x$ is endogenously revealed to match a given share of exporting firms at the steady state. Further, \cite{Lincoln_McCallum2018} document the large increase in the number of exporting firms in the US between the mid 1980s et the mid 2000s, with a share of exporting firms raising by 52\% over this period. Accordingly, we will assess the effects of the trade liberalization assuming a joined reduction in both the variable transport costs ($\tau, t$, based on our empirical estimates) and the fixed export cost $f_x$. Specifically, we endogenously determine the initial value of $f_x$ such that the initial steady state, with 1974 values of transport costs implies a share of exporting firms equal to 4\%, as documented by \cite{BEJK-AER-03}. In the final steady state, $f_x$ will be revealed such that this share of exporting plants has increased by 52\% (i.e., from 4\% to 6\%), based on \cite{Lincoln_McCallum2018}.

@@

\textbf{A DEVELOPPER}

>>>>

\begin{table}[htbp]
 \centering
\caption{Transport costs estimates: summary} \vspace{5mm} \label{tab:summary_results}
	\input{Table1_reshaped.tex}
		\begin{tablenotes}
		\tiny
		\item Statistics are obtained weighting each observation by its value relative to total trade flows.
		\item 1989 trade by air is excluded
		%\item The additive term is expressed in fraction of fas price.
		\item For the  4-digit model, statistics for observed data have been calculated for the same set of years as used for estimation, i.e.
		1974, 1981, 1989, 2001, 2009, 2013, 2017 and 2019
		\item \textbf{Model (a): With ad-valorem transport costs only}
		\item \textbf{Model (b): With additive and ad-valorem transport costs}
	\end{tablenotes}
\end{table}

@@

\begin{table}[htbp]
  \centering
  \caption{Calibration (1)} \label{tab:calib_horsTC}
\begin{center}
	\input{donnees_calibration.tex}
\end{center}
{\parbox[l]{12cm}{ \vspace{4pt}\footnotesize{Notes: $f_x$ can take two values, depending on the share of exporters considered that might differ between the initial steady state (4\%, based on early 1980s' value) and the final steady state (6\%, based on 2000's value.)}}}
\end{table}

Following \cite{ghironi}, $f$ such that all firms produce in autarky (i.e., such that $\varphi^{\ast,a} = \varphi_{\text{min}}$. The calibration of the fixed export cost obeys the following logic. As in \cite{ghironi}, $f_x$ is endogenously revealed to match a given share of exporting firms at the steady state. Further, \cite{Lincoln_McCallum2018} document the large increase in the number of exporting firms in the US between the mid 1980s et the mid 2000s, with a share of exporting firms raising by 52\% over this period. Accordingly, we will assess the effects of the trade liberalization assuming a joined reduction in both the variable transport costs ($\tau, t$, based on our empirical estimates) and the fixed export cost $f_x$. Specifically, we endogenously determine the initial value of $f_x$ such that the initial steady state, with 1974 values of transport costs implies a share of exporting firms equal to 4\%, as documented by \cite{BEJK-AER-03}. In the final steady state, $f_x$ will be revealed such that this share of exporting plants has increased by 52\% (i.e., from 4\% to 6\%), based on \cite{Lincoln_McCallum2018}.\smallskip

@@

\textbf{Lise, 06-09-2021: Stop here, changer la calibration}

### 2021-09-06 redaction/JEGeo/revision_JEGeo/revised_article/donnees_calibration.tex
avec le .tex corrigé des bugs

\begin{tabular}{lll}
& Value & Reference\\
\hline
$\sigma$ & 4 & \cite{Irrazabal_2015}\\
$f_e$ & 1 & \cite{ghironi}\\
$f$ & 0.033 & \cite{ghironi} \\
$L$ & 1 & Arbitrary\\
$\delta$ & 0.1 & \cite{ghironi}, \cite{Irrazabal_2015}\\
$k$ & 4 \\
$\varphi_{\text{min}}$ & 1 & \cite{ghironi}, \cite{Irrazabal_2015}\\ \hline
\multicolumn{3}{l}{Fixed export cost } \\
$f_x $ & XXX & Share of exporting firms = 4\% (BEJK, 2003) \\
& XXX& Share of exporting firms = 6\% (\cite{Lincoln_McCallum2018}
\hline
\end{tabular}

>>>>

\begin{tabular}{lll}
& Value & Reference\\
\hline
$\sigma$ & 4 & \cite{Irrazabal_2015}\\
$f_e$ & 1 & \cite{ghironi}\\
$f$ & 0.033 & \cite{ghironi} \\
$L$ & 1 & Arbitrary\\
$\delta$ & 0.1 & \cite{ghironi}, \cite{Irrazabal_2015}\\
$k$ & 4 \\
$\varphi_{\text{min}}$ & 1 & \cite{ghironi}, \cite{Irrazabal_2015}\\ \hline
\multicolumn{3}{l}{Fixed export cost } \\
$f_x $ & XXX & Share of exporting firms = 4\% (BEJK, 2003) \\
& XXX& Share of exporting firms = 6\% (\cite{Lincoln_McCallum2018}) \\
\hline
\end{tabular}
